Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-14 paper/5_concl.tex
edits with MG

International relations is about the interactions, relationships, and dependencies among countries or other important international actors. This is particularly true of scholarship in the tradition of the Correlates of War Project, but it is by no means limited to it.\footnote{See \cite{singer:1972} for an early description of the project and also see the project's Web site for an history and more recent efforts \url{http://www.correlatesofwar.org/}.} Many scholars have debated the use and abuse of dyadic data.\footnote{One recent on-line symposium can be found at \url{http://bit.ly/2wB2hab}.} A broad survey of the IR literature makes it clear that scholars find dyadic data to be an essential touchstone in the study of international relations \citep{erikson:pinto:2014,aronow:etal:2015}. \textcolor{blue}{Our findings bolster a growing recognition in the field of International Relations that interdependence plays an important role not just in terms of statistical estimations, but in the ways that scholars theorize about internationally relevant politics. Scholars have demonstrated the theoretical importance of interdependence through research on conflict \citep{dorff:etal:2020}, economic interdependence \citep{maoz:2009a}, and international treaties \citep{kinne:2013} among other topics.}

>>>>

International relations is about the interactions, relationships, and dependencies among countries or other important international actors. This is particularly true of scholarship in the tradition of the Correlates of War Project, but it is by no means limited to it.\footnote{See \cite{singer:1972} for an early description of the project and also see the project's Web site for an history and more recent efforts \url{http://www.correlatesofwar.org/}.} Many scholars have debated the use and abuse of dyadic data.\footnote{One recent on-line symposium can be found at \url{http://bit.ly/2wB2hab}.} A broad survey of the IR literature makes it clear that scholars find dyadic data to be an essential touchstone in the study of international relations \citep{erikson:pinto:2014,aronow:etal:2015}. \textcolor{blue}{Our findings bolster a growing recognition in the field of International Relations that interdependence plays an important role not just in terms of statistical estimations, but in the ways that scholars theorize about internationally relevant politics. Scholars have demonstrated the theoretical importance of interdependence through research on intrastate conflict \citep{dorff:etal:2020}, interstate bargaining \citep{gallop:2017}, economic interdependence \citep{maoz:2009a}, and international treaties \citep{kinne:2013} among other topics.}

### 2020-02-14 revisionMemo/rev2.tex
edits with MG

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
%		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
%		Reference papers that have thought about what happens when we get the wrong W
%		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
%		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach
In the appendix, we compare our models approach in simulations to a number of other methods of dealing with dependencies, notably LIST THEM. In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern. Further, spatial lags are likely to be particularly complex in the cases of dyadic data because we would need an appropriate measure of dyadic similarity (see \citet{plumper:neumayer:2010}).

NOTE TO US: Reading this Q again, do they want us to redo the simulation such that the variance is coming from spatial stuff?

>>>>

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
\item \textcolor{blue}{ \emph{
The reviewer raises an important connection to the spatial literature. The types of geographic dependencies in international relations are generally monadic in nature -- civil war spreads from Rwanda to Uganda, or protest from Lebanon to Syria. With dyadic data, however, we cannot use the common geographic adjacency matrices used for normal spatial econometrics, because in dyadic data a W matrix would need to specify how dyad i,j relates to dyad k,l (for every i,j,k,l). In an effort to speak to other known approaches in the literature, we compare our model via simulations to a number of other methods of dealing with dependencies, notably LIST THEM. In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern (see \citet{plumper:neumayer:2010} for a more in-depth discuss on spatial lags). 
}}

%		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
%		Reference papers that have thought about what happens when we get the wrong W
%		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
%		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach
